\documentclass{report}

\begin{document}
{\bf KEYS}:
\begin{itemize}
\item ask which aspect will I concentrate on?
\item collision risk assesument accuracy
\item ship encounter operation (situation awareness)
\item risk assessment methodology
\item COLREGs
\item Kalman filter is essntially a mean-square error estimator, and it has much in common with the {\it chi-square}. The {\it chi-square} merit function is a maximum likelihood function. Kalman filter is also known as a recursiv least squares (RLS) filter.
\end{itemize}

Questions that may appear
\begin{enumerate}
\item Tell me more about yourself?
\item Do you have wife?
\item Why not and how to map those knots to robots
\item It seems you have a traditional maritime history
\item Why would you like to apply for this position?
\end{enumerate}

What makes me the right candidate for this PhD project?
\begin{description}
\item Advanced ship predictor: background in sensor raw data manipulation, handling with lots of different sensors. I have great experience in underwater communication system and navigation system. Field trip, project in estimating and comparing with two different systems. sd2709 simulation of turning and zig-zag manoeuvre using PID control to make it yaw-sway stable. Go check those manoeuvring equations (TMR4220 & TMR4217)
\item Experimental evaluation: at Marintek, several experimental testings were conducted such as propeller open water testing and ship resistance and propulsion test. A sail trial has also been conducted in last december in stockhlom sea. 
\item Collision risk assessment methodology: Human risk, little knowledge about risk though, but I am eager to learn.
\end{description}

\pagebreak
\chapter{Kalman filter}
The filter is constructed as a mean squared error minimiser, and also relates to maximum likelihood statistics. Wiener's solution uses both thee autocorrelation and the crosscorrelation of the received signal with the original data to derive an impulse response for the filter. Instead, Kalman uses state space which can hence be applied to a wide range of applications. Kalman enable the filter to be used as either a smoother, a filter or a predictor.
\section{State space derivation}


\end{document}
